---
title: "First Assignment"
author: "Dylan Culp"
date: "9/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For this assignment, I chose to look at household-level data related to housing (costs and physical characteristics) in Rhode Island. I did not collect this data with a clear research question in mind, but hope to see if the following variables can reveal some interesting trends:

  1. Lot size (categorical): ACR
  2. Units in structure (categorical): BLD
  3. Number of bedrooms (continuous): BDSP
  4. Property taxes paid in prior year (continuous): TAXAMT
  5. Gross rent as % of resident income (continuous): GRPIP
  6. Monthly electricity cost (continuous): ELEP

I then decided to filter out property owners, to focus allow for the gross rent variable. By including only observations where TAXAMT = -1, I was able to select non-property tax paying households. This may not be perfectly synonymous with renter households, however. Here is the code:
```{r}
hh_data <- get_pums(variables = c("ACR",
+                                   "BLD",
+                                   "BDSP",
+                                   "TAXAMT",
+                                   "GRPIP",
+                                   "ELEP"),
+                     state = "RI",
+                     year = 2018,
+                     survey = "acs1",
+                     recode = TRUE) %>%
+     filter(TAXAMT == -1) %>%
+     select(ACR_label, BLD_label, BDSP, GRPIP, ELEP)
```

After this filter, the population is defined as "non-property tax paying households in Rhode Island", and the n=3480. Although the first 10 rows are identical, the rest of the dataset does encompass more diverse data.  

```{r}
hh_data
```


