---
title: "Assignment 3"
author: "Dylan Culp"
date: "9/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
```

Loading my data from prior projects:
```{r}
king_tracts<-read_csv("king_tracts.csv")
attach(king_tracts )

```
1. Correlations (Continuous-continuous)

Four of my variables are continuous, which calls for six correlation tests between these variables: 
```{r}
cor.test(king_tracts$pct_rental, king_tracts$med_age)
cor.test(king_tracts$pct_rental, king_tracts$avg_hh_size)
cor.test(king_tracts$pct_rental, king_tracts$tot_pop)
cor.test(king_tracts$avg_hh_size, king_tracts$tot_pop)
cor.test(king_tracts$avg_hh_size, king_tracts$med_age)
cor.test(king_tracts$tot_pop, king_tracts$med_age)

```


Percent renters and Median Age

  Correlation: -0.574732 
  P value: <2.2e-16 (statistically significant)

Percent renters and Average Household Size:
  Correlation: -0.64888811
  P value: <2.2e-16 (statistically significant)
  
Percent Renters and total Population:
  Correlation: 0.01471284
  P value: 0.7701 (not statistically significant)
  
Average housheold size and total population:
  Correlation: 0.11528194
  P value: 0.0216 (statistically significant)
  
Average household size and median age:
  Correlation: 0.03455301 
  P value:0.4924 (not statistically significant) 
  
Total population and median age:
  Correlation: 0.21226327
  P value: 2.002e-05 (statistically significant)




Binary and continuous: Two Sample T Test

I have one binary variable (whether the tract is rural or urban), and I will use the Two Sample test to assess its relationship with the four continuous variables.
```{r}

t.test(pct_rental ~ rural, data = king_tracts)
t.test(avg_hh_size ~ rural, data = king_tracts)
t.test(tot_pop ~ rural, data = king_tracts)
t.test(med_age ~ rural, data = king_tracts)

```
Key figures:

Rural and Percent Renters
  T value: 6.461
  P value: 0.01236 (statistically significant)

Rural and Average Household Size
  T value: 0.25081
  P value: 0.8244 (not statistically significant)

Rural and Total Population
  T value: 0.19533
  P value: 0.8627 (not statistically significant)
  
Rural and Median Age: 
  T value: -3.5737
  P value: 0.06847 (not statistically significant)




Two categorical Values: Chi Squared

I am using the Chi Squared for the relationship between my only two categorical values: Rural and Majority race/ethnicity

```{r}
chisq.test(king_tracts$rural, king_tracts$majority_race_eth)
```
X squared value:
P value= 0.6584 (not statistically significant)



Anova Test: Categorical and Continuous Variables

Lastly, I will use this test to measure the relationship between the multivariate categorical (majority race/ethnicity) and four continuous variables.

```{r}
summary(aov(pct_rental ~ majority_race_eth, data=king_tracts))
summary(aov(avg_hh_size ~ majority_race_eth, data=king_tracts))
summary(aov(tot_pop ~ majority_race_eth, data=king_tracts))
summary(aov(med_age ~ majority_race_eth, data=king_tracts))
```


