---
title: "Assignment 2"
author: "Dylan Culp"
date: "9/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
```

I decided to use my data for King County Washington from VIS (instead of my RI data from last week), since I found the figures here more interesting. Each of these data are represented at the tract level.

```{r}
king_tracts<-(read_csv("king_tracts.csv", col_names =c("X1", "GEOID", "rural", "majority_race_eth", "pct_rental", "avg_hh_size", "tot_pop", "med_age")))

```

Continuous Variables

1. Percentage of renters by tract

```{r}
ggplot(king_tracts, aes(x = pct_rental))+
  geom_histogram()

```
```{r}
mean(pct_rental)
sd(pct_rental)
t.test(pct_rental)
quantile(pct_rental)

```

Sample mean: 35.4%
Sample std dev: 19.3%
95% Confidnence interval mean: between 33.6 and 37.3%
IQ range: 20% to 49%


2. Average household size
```{r}
ggplot(king_tracts, aes(x = avg_hh_size))+
  geom_histogram()
```


```{r}
mean(avg_hh_size)
sd(avg_hh_size)
t.test(avg_hh_size)
quantile(avg_hh_size)
```
Sample mean: 2.46
Sample std dev: 0.43
95% Confidnence interval mean: between 2.41 and 2.50
IQ range: 2.21 to 2.77



3. Total Population per tract
```{r}
ggplot(king_tracts, aes(x = tot_pop))+
  geom_histogram()
```

```{r}
mean(tot_pop)
sd(tot_pop)
t.test(tot_pop)
quantile(tot_pop)
```

Sample mean: 4865
Sample std dev: 1486
95% Confidnence interval mean: between 4718 and 5011
IQ range: 3759 to 5797


4. Median Age
```{r}
ggplot(king_tracts, aes(x = med_age))+
  geom_histogram()
```

```{r}
mean(med_age)
sd(med_age)
t.test(med_age)
quantile(med_age)
```

Sample mean: 37.9
Sample std dev: 5.1
95% Confidnence interval mean: between 37.4 and 38.4
IQ range: 34.5 to 40.9



Categorical Variables

Is the tract rural or urban?

```{r}
t.test(rural)
```
```{r}
t.test(majority_race_eth, TRUE)
```